The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-03-31 methods/ms.tex
new paper draft - cores->clumps

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm
continuum survey of \bgpsarea\ square degrees of the Galactic Plane in
the 1st, 2nd, and 3rd quadrants.  The BGPS represents the first large
area, systematic survey of the Galactic Plane in the (sub)millimeter
continuum without pre-selected targets.  The survey has detected
\ncores\ cores to a limiting depth of between \bgpsdepthlow\ and
\bgpsdepthhigh\ mJy RMS.  This paper details the survey observations
and methods.  We treat carefully the comparison of the survey pointing
and flux calibration and and serves as a companion to the public data
release through NASA's Infrared Processing and Analysis Center (IPAC).
We anticipate that the BGPS will be useful as a finder chart for ALMA
and as a long-wavelength complement to {\em Herschel}-HiGAL.

@@

Millimeter-wavelength continuum surveys of the Galactic plane provide
the best way to identify high-column density cores and clumps where
planets, stars, and star clusters form.  Such data can locate and lead
to the measurement of the physical properties of cores un-biased by
selection effects such as the presence of embedded stars, star
clusters, infrared sources, masers, or radio continuum emission.
Galaxy-wide surveys are essential for measuring the impacts of the
environment on core properties and star formation activity.  Do core
properties vary with location in or out of spiral arms?  Do core
properties vary with Galactocentric distance?  Do they depend on the
level of nearby star formation activity?  Galactic plane surveys of
mm-wavelength dust continuum emission provide the most efficient tool
for the identification of potential or active sites of star formation,
including the rare objects where the most massive stars and cluster
are, or soon will be, forming.  Dust continuum surveys of the Galaxy
provide essential ``ground truth'' required for the analysis of distant
galaxies where where individual clouds and cores are not resolved and
only galaxy-wide average quantities can be measured.

@@

A crucial step in the observational study of star and cluster
formation is identification and characterization of the cloud cores
which will soon form or are actively forming stars.  Massive stars and
clusters form from high-density cloud cores with very large column
densities and extinctions $A_V > $ 100.  Thus, such cloud cores are
best investigated at millimeter and sub-millimeter wavelengths.
However, the interpretation of various gas tracers that produce
emission lines in this portion of the spectrum is very difficult.
Although in principle, spectral lines provide excellent diagnostics of
line-of-sight motions, temperatures, and densities in a cloud,
variations in tracer abundances caused by depletions and complex
chemical processing, uncertainties in excitation conditions, and the
impacts of radiation fields and shocks make the derivation of column
densities, masses, and other physical properties of cloud cores very
difficult.  The continuum emission from warm dust provides a more
reliable tracer of the column densities and core masses.

@@

This survey presents the results of one of the first wide-area,
untargeted surveys of the Galactic Plane in the millimeter continuum.
We have used the 144 element Bolocam focal plane array, mounted at the
Cassegrain focus of the 10 meter diameter sub-mm telescope at the
Caltech Sub-millimeter Observatory (CSO), to survey over \bgpsarea\
square degrees of the northern Galactic plane at a wavelength of 1.1
mm in the dust continuum.  Figure \ref{fig:Coverage} shows the
coverage of the \bgps.  Maps of the entire BGPS are presented in
Figure \ref{fig:BGPSMontage}.  We have detected \ncores\ cores in the
surveyed fields, providing an unbiased sample of cores suitable for
multi-wavelength and high-resolution studies with existing telescopes
and future facilities.  The core catalog is described in a companion
paper \citep{rosolowsky09}.

>>>>

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm
continuum survey of \bgpsarea\ square degrees of the Galactic Plane in
the 1st, 2nd, and 3rd quadrants.  The BGPS represents the first large
area, systematic survey of the Galactic Plane in the (sub)millimeter
continuum without pre-selected targets.  The survey has detected
\ncores\ clumps to a limiting depth of between \bgpsdepthlow\ and
\bgpsdepthhigh\ mJy RMS.  This paper details the survey observations
and methods.  We treat carefully the comparison of the survey pointing
and flux calibration and and serves as a companion to the public data
release through NASA's Infrared Processing and Analysis Center (IPAC).
We anticipate that the BGPS will be useful as a finder chart for ALMA
and as a long-wavelength complement to {\em Herschel}-HiGAL.

@@

Millimeter-wavelength continuum surveys of the Galactic plane provide
the best way to identify high-column density clumps and clumps where
planets, stars, and star clusters form.  Such data can locate and lead
to the measurement of the physical properties of clumps un-biased by
selection effects such as the presence of embedded stars, star
clusters, infrared sources, masers, or radio continuum emission.
Galaxy-wide surveys are essential for measuring the impacts of the
environment on clump properties and star formation activity.  Do clump
properties vary with location in or out of spiral arms?  Do clump
properties vary with Galactocentric distance?  Do they depend on the
level of nearby star formation activity?  Galactic plane surveys of
mm-wavelength dust continuum emission provide the most efficient tool
for the identification of potential or active sites of star formation,
including the rare objects where the most massive stars and cluster
are, or soon will be, forming.  Dust continuum surveys of the Galaxy
provide essential ``ground truth'' required for the analysis of distant
galaxies where where individual clouds and clumps are not resolved and
only galaxy-wide average quantities can be measured.

@@

A crucial step in the observational study of star and cluster
formation is identification and characterization of the cloud clumps
which will soon form or are actively forming stars.  Massive stars and
clusters form from high-density cloud clumps with very large column
densities and extinctions $A_V > $ 100.  Thus, such cloud clumps are
best investigated at millimeter and sub-millimeter wavelengths.
However, the interpretation of various gas tracers that produce
emission lines in this portion of the spectrum is very difficult.
Although in principle, spectral lines provide excellent diagnostics of
line-of-sight motions, temperatures, and densities in a cloud,
variations in tracer abundances caused by depletions and complex
chemical processing, uncertainties in excitation conditions, and the
impacts of radiation fields and shocks make the derivation of column
densities, masses, and other physical properties of cloud clumps very
difficult.  The continuum emission from warm dust provides a more
reliable tracer of the column densities and clump masses.

@@

This survey presents the results of one of the first wide-area,
untargeted surveys of the Galactic Plane in the millimeter continuum.
We have used the 144 element Bolocam focal plane array, mounted at the
Cassegrain focus of the 10 meter diameter sub-mm telescope at the
Caltech Sub-millimeter Observatory (CSO), to survey over \bgpsarea\
square degrees of the northern Galactic plane at a wavelength of 1.1
mm in the dust continuum.  Figure \ref{fig:Coverage} shows the
coverage of the \bgps.  Maps of the entire BGPS are presented in
Figure \ref{fig:BGPSMontage}.  We have detected \ncores\ clumps in the
surveyed fields, providing an unbiased sample of clumps suitable for
multi-wavelength and high-resolution studies with existing telescopes
and future facilities.  The clump catalog is described in a companion
paper \citep{rosolowsky09}.
